The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2019-09-09 tex/VHzQ.tex
Fixes to make correctly

\begin{figure}
%%trim=l b r t
  \includegraphics[width=8.0cm, clip, trim=0mm 25mm 0mm 40mm]
  {../data/WSA_VSA/CoverageMaps_VHzQ_forpaper.pdf}
  \centering
  \caption[]
  {The coverage maps for VHS (DR6; orange), UHS (DR1; olive), VIKING (DR5; blue) and ULAS (DR11; red), the most recent public releases of the 4 main surveys. The VH$z$Qs are given by black dots.}
  \label{fig:coverage}
\end{figure}

@@

\begin{table*}
\begin{tabular}{l r r r r r}
\hline  \hline
QSO & ra & dec & difference & isCRDiff & Issue \\
 & deg & deg & arcsec & &  \\
\hline
OGLEJ015531-752807 & +28.8792083 & -75.4686111 & 1.1 & No & 1 \\
%% Same name diff pos/redshift from v1
PSOJ009.7355-10.4316 & +9.7355079 & -10.4316386	& 0. & Yes & 3 \\
ATLASJ025.6821-33.4627 & +25.6821972 & -33.4626300 & 0. & Yes & 3 \\ 
SDWISEJ0155+0415 & +28.8886666 & +4.2518725	& 0. & Yes & 3 \\
PSOJ065.4085-26.9543 & +65.4085370 & -26.9543351 & 0. & Yes & 3 \\ 
VDESJ0454-4448 & +73.5074500 & -44.8086400 & 0.	& Yes & 3 \\ 
DELSJ1048-0109 & +162.0795417 & -1.1611694 & +12.1 & Yes & 2,3,4 \\
SDSSJ1306+0356 & +196.5344701 & +3.9406556 & 0.	& Yes & 3 \\
PSOJ217.0891-16.0453 & +217.0891328	& -16.0453608 & 0. & Yes & 3 \\
SHELLQsJ1429-0002 & +217.3342500 & -0.0353889 & +150.0 & Yes & 2 \\
DELSJ1559+2212 & +239.7878750 & +22.2040083	& +3.0 & Yes & 2 \\ 
ATLASJ332.8017-32.1036 & +332.8017500 &	-32.1035556	& +3.2 & Yes & 2,3 \\
PSOJ340.2041-18.6621 & +340.2041700	& -18.6621700 & 0. & Yes & 3 \\ 
VIKJ2318-3113 & +349.5764625 &-31.2295417 & 239.9 & Yes & 2,3 \\
PSOJ359.1352-06.3831 & +359.1352149	& -6.3831264 & 0. & Yes & 3 \\
%%Krisztina wrong\ldots
SDSSJ1621+5155 & +245.2538300 & +51.9302200	& 0. & No & 5 \\
DELSJ1135+5011 & +173.7872080 & +50.1924999	& 0. & No & 5 \\
DELSJ0839+3900 & +129.9453330 & +39.0031944	& 0. & No & 5 \\
%% More complex 
SDSSJ0835+3227 & --- & --- & --- & No & 6 \\
VA-13492 & --- & --- & --- & No & 6 \\
\hline  
\hline  \hline
\end{tabular}
\caption{{\bf QSOs in disagreement between RC and Perger or which have been
updated since the submitted paper.
This table shows all of the QSOs where there has been a disagreement or a
change. All of those marked 'Yes' were in the submitted paper and have been
changed since, and the final column lists the reason(s) for inclusion in the
table. The numbers refer to the following issues:
\begin{itemize}
	\item 1) Coordinate update in original reference, from submitted to accepted; 
	\item 2) Coordinate different in RC submitted
	\item 3) Redshift different in RC submitted, typically very small changes. 
	\item 4) Our coords incorrect, but KP had 2 entries, one also incorrect
	\item 5) Coordinates incorrect in KP.
	\item 6) Two objects with similar looking coordinates and identical redshifts.
	These appear to be incorrect entries further back in the literature. 
\end{itemize}  
}}
\label{tab:disagree_objs}
\end{table*}

>>>>

\begin{figure}
%%trim=l b r t
  \includegraphics[width=8.0cm, clip, trim=0mm 25mm 0mm 40mm]
  {../data/WSA_VSA/CoverageMaps_VHzQ_forpaper/CoverageMaps_VHzQ_forpaper.pdf}
  \centering
  \caption[]
  {The coverage maps for VHS (DR6; orange), UHS (DR1; olive), VIKING (DR5; blue) and ULAS (DR11; red), the most recent public releases of the 4 main surveys. The VH$z$Qs are given by black dots.}
  \label{fig:coverage}
\end{figure}

@@

\begin{table*}
\begin{tabular}{l r r r r r}
\hline  \hline
QSO & ra & dec & difference & isCRDiff & Issue \\
 & deg & deg & arcsec & &  \\
\hline
OGLEJ015531-752807 & +28.8792083 & -75.4686111 & 1.1 & No & 1 \\
%% Same name diff pos/redshift from v1
PSOJ009.7355-10.4316 & +9.7355079 & -10.4316386	& 0. & Yes & 3 \\
ATLASJ025.6821-33.4627 & +25.6821972 & -33.4626300 & 0. & Yes & 3 \\ 
SDWISEJ0155+0415 & +28.8886666 & +4.2518725	& 0. & Yes & 3 \\
PSOJ065.4085-26.9543 & +65.4085370 & -26.9543351 & 0. & Yes & 3 \\ 
VDESJ0454-4448 & +73.5074500 & -44.8086400 & 0.	& Yes & 3 \\ 
DELSJ1048-0109 & +162.0795417 & -1.1611694 & +12.1 & Yes & 2,3,4 \\
SDSSJ1306+0356 & +196.5344701 & +3.9406556 & 0.	& Yes & 3 \\
PSOJ217.0891-16.0453 & +217.0891328	& -16.0453608 & 0. & Yes & 3 \\
SHELLQsJ1429-0002 & +217.3342500 & -0.0353889 & +150.0 & Yes & 2 \\
DELSJ1559+2212 & +239.7878750 & +22.2040083	& +3.0 & Yes & 2 \\ 
ATLASJ332.8017-32.1036 & +332.8017500 &	-32.1035556	& +3.2 & Yes & 2,3 \\
PSOJ340.2041-18.6621 & +340.2041700	& -18.6621700 & 0. & Yes & 3 \\ 
VIKJ2318-3113 & +349.5764625 &-31.2295417 & 239.9 & Yes & 2,3 \\
PSOJ359.1352-06.3831 & +359.1352149	& -6.3831264 & 0. & Yes & 3 \\
%%Krisztina wrong\ldots
SDSSJ1621+5155 & +245.2538300 & +51.9302200	& 0. & No & 5 \\
DELSJ1135+5011 & +173.7872080 & +50.1924999	& 0. & No & 5 \\
DELSJ0839+3900 & +129.9453330 & +39.0031944	& 0. & No & 5 \\
%% More complex 
SDSSJ0835+3227 & --- & --- & --- & No & 6 \\
VA-13492 & --- & --- & --- & No & 6 \\
\hline  \hline
\end{tabular}
\caption{{\bf QSOs in disagreement between RC and Perger or which have been
updated since the submitted paper.
This table shows all of the QSOs where there has been a disagreement or a
change. All of those marked 'Yes' were in the submitted paper and have been
changed since, and the final column lists the reason(s) for inclusion in the
table. The numbers refer to the following issues:
1) Coordinate update in original reference, from submitted to accepted; 
2) Coordinate different in RC submitted;
3) Redshift different in RC submitted, typically very small changes;
4) Our coords incorrect, but KP had 2 entries, one also incorrect;
5) Coordinates incorrect in KP;
6) Two objects with similar looking coordinates and identical redshifts. These
appear to be incorrect entries further back in the literature;}
}
\label{tab:disagree_objs}
\end{table*}
